---
title: "Counting Proteins"
author: "ebecerra"
date: "`r Sys.Date()`"
output: pdf_document
---

## Reading the data

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


```{r}
source("filter_blasts.R")
```

## Domain Description

### YwqJ `WP_003243987.1`
1. _LXG_ - `IPR006829`
2. _PT-TG_ - `IPR027797`
3. _YwqJ-like_ - `IPR025968`

### YwqL `WP_003243213.1`
1. _Endonuclease-V_ - `IPR007581`



## How many unique proteins remain after filtering?

### Which domains use to filter ...

```{r}
FILTER_main <- list(
  WP_003243987.1 = c("IPR006829", "IPR025968"),
  WP_003243213.1 = c("IPR007581")
)


FILTER_noEndoV <- list(
  WP_003243987.1 = c("IPR006829", "IPR025968")
)

FILTER_all <- list(
  WP_003243987.1 = c("IPR006829", "IPR027797", "IPR025968"),
  WP_003243213.1 = c("IPR007581")
)
```


### Counting

```{r}
count_proteins <- function(FILTER, tbl) {
  tbl |>
    group_by(q_alias, query, pid) |>
    summarise(domains = list(domain)) |>
    filter(check_domains(query, domains, FILTER)) |>
    nrow()
}
```


```{r}
results <- list(FILTER_noEndoV, FILTER_main, FILTER_all) |>
  map_int(count_proteins, mappings) |>
  `names<-`(c("no_EndoV", "main", "all"))

results
```

### Results

#### No _EndoV_

Without using the _Endonuclease V_ domain,
the number of unique proteins is: `r results["no_EndoV"]`

+ $YwqJ \supseteq \{"IPR006829", "IPR025968"\}$

#### Suggested filtering

Using the suggested domains,
the number of unique proteins is: `r results["main"]`

+ $YwqJ \supseteq \{"IPR006829", "IPR025968"\}$
+ $YwqL \supseteq \{"IPR007581"\}$

#### Using all domains

Using the all domains,
the number of unique proteins is: `r results["all"]` 

+ $YwqL \supseteq \{"IPR007581"\}$
+ $YwqJ \supseteq \{"IPR006829", "IPR027797", "IPR025968"\}$
